Bayesian exponential random graph modeling of KWL Burial network

### 2020-04-13 analysis/paper/paper.Rmd
edit the ERGM para and add references

<!--current approaches to network analysis-->
Exponential Random Graph Models (ERGMs) are an important family of statistical model for network analysis to describe the formation of ties in a network. In traditional statistical model for network, a dyad, the pair of nodes, is measured by the presence of a tie according to the attributes of the nodes or ties, where each predictor variable for forming a tie is measured separately. In contrast to traditional model where variables not interacting with each other, ERGMs assumes the formation of a tie is influenced by the presence or absence of other ties or attributes of nodes and ties (Robins et al. 2007). In a network using ERGMs, predictor variables, called "network statistics", are direct functions of the ties themselves that the probability of occurrence of the configuration of ties can be hypothesized [@Morris2008]. This approach enables networks to be constructed in a variety of assumption and contexts to model social network in the past using archaeological data [@Amati2019]. However, ERGMs are difficult to compute because their normalizing constant depending on model parameters is intractable. A Bayesian framework allows for parameter inference using Markov chain Monte Carlo (MCMC) strategies which avoid the need for computationally intensive calculations of the normalizing constants [@Caimo2011].

>>>>

<!--current approaches to network analysis-->
Exponential Random Graph Models (ERGMs) are an important family of statistical model for expressing properties of network structures with a focus directly on possible ties between nodes by viewing them as random variables [@Robins2007]. In traditional statistical model for network, each predictor variable for forming a tie between two nodes is measure separately by the presence of a tie without considering interactions among ties [@Morris2008]. By contrast, statistical models assumes social networks as dependent variables that can represent the network dependencies between tie variables [@Snijders2011]. In a network generated by ERGMs, the formation of a tie is influenced by the presence or absence of other ties or attributes of nodes/ties. Predictor variables, called network statistics, such as reciprocity, transitivity, homophily, are direct functions of the ties themselves where the probability of occurrence of the configuration of ties can be specified and hypothesized [@Morris2008; @Robins2007]. With the development of Markov chain Monte Carlo (MCMC) algorithms that produce approximate maximum likelihood estimators and graph statistics for further specification of transitivity and heterogeneity, ERGMs can deal with complicated dependence patterns observed at one moment in time [@Snijders2006]. The advantage of networks specification under assumptions and contexts can be useful to explain archaeological network in a given time. @Amati2019 demonstrate the use of ERGMs to reconstruct networks consist of a set of sites in the Caribbean during the period AD 100–400. They found out the structure of network can be efficiently explained by multiple interdependent mechanisms instead of hypotheses of distance and cultural homophily exclusively. However, they also point out some limitation of ERGMs

However, two major limitations ERGMs are difficult to compute because their normalizing constant depending on model parameters is intractable. A Bayesian framework allows for parameter inference using Markov chain Monte Carlo (MCMC) strategies which avoid the need for computationally intensive calculations of the normalizing constants [@Caimo2011].
